---
title: "Resampling"
author: "Christopher Brown"
date: "October 5, 2015"
output: html_document
---


```{r}
set.seed(314159)
<<<<<<< HEAD
library(plyr)
data("baseball")
=======
install.packages('plyr')
# library(plyr)
data(baseball,package="plyr")
>>>>>>> a4ce92f2347c0e58599cc3811e0046c345ff1fbf
```


Use the `baseball` data set from the `plyr` package for the following problem.

A very simple model to predict the number of at-bats/game **each** player has per game is given by: 
 
     abpg = sum(ab)/sum(g)  # 3.10
     

- Show that this is a bad:

```{r}
attach(baseball)
library(ggplot2)

<<<<<<< HEAD
q_err <- quote(ab/g-abpg)
q_abpg <- quote(sum(ab)/sum(g))

mean(eval(q_err,baseball),na.rm = TRUE)  #-0.65
hist(eval(q_err,baseball))

#residuals are not mean 0
=======
abpg = with( baseball, sum(ab)/sum(g) )

>>>>>>> a4ce92f2347c0e58599cc3811e0046c345ff1fbf
```



- Create a better model using only number of games (g) as a predictor

```{r}
any(g==0)
baseball <- baseball[g!=0]
fit <- lm(ab~g+0,baseball)
summary(fit)
```


- Calculate the "Apparent" *RMSE* of this model.    

```{r}
#Hint: Look to applyfunction :apply(1:5,function(x){...fit calculate error...})   mean()  baseball[x=={}]


```


Using only Recreate the model, providing a new estimate for `ab/g` and the RMSE, using:
- 5-Fold CV
- Bootstrap

```{r}
#Hint: sample (replace=True)


```

